Untitled

### 2018-08-17 PaperCode.Rmd
Cleaning and don't ruin postocdes

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))

rm(PstCdLSOA.raw)
```

#MSOA to LAD
```{r}
MSOAtoLAD <- EW2 %>%
  group_by(MSOA11CD, LAD11CD, LAD11NM) %>%
  summarise(TotMSOA = n(),
         Homes = sum(Homes),
         Region = first(Region)) %>%
  arrange(-TotMSOA) %>%
  group_by(MSOA11CD) %>%
  mutate(counts = n()) %>%
  summarise(LAD11CD = first(LAD11CD),
            TotMSOA = first(TotMSOA),
            counts = first(counts),
            LAD11NM = first(LAD11NM),
            Homes = first(Homes),
            Region = first(Region))
```

@@

##MSOA Bootstrap
Used for most of the analysis
```{r}
setwd(file.path(basewd, "BootstrapMSOA"))
BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
BootStrapMSOA <- LoadBootstrapData()

@@

```{r}
CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>%  
  group_by(ID, Class) %>%
  summarise(Homes = sum(Homes), 
            LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(LowUseDistrib = LowUse/sum(LowUse),
         HomesDistrib = Homes/sum(Homes)) %>%
  mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
         HomesRatio1 = (HomesDistrib/0.25)-1,
         LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
    ungroup
}

LADS<-DATAdf%>%
  group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM)) %>%
  arrange(LAD11NM)

#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(Class = CountryClass)

BootStrapQuartiles$E09000020  %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
BootStrapQuartiles$E08000032 %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
All_data_class %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "LowUseRatio2")

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio1") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

```{r}
setwd(file.path(basewd, "VOA data"))

#Creates Tourism dataframe at LSOA level
Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
                          delim = "*", col_names = F) %>%
  mutate(X15 = gsub(" ", "", X15)) %>%
  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
  filter(!is.na(LAD11CD)) %>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
   group_by(LSOA11CD, X6) %>%
  summarise(Tourism = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD),
            Pop = first(Pop),
            Guest = sum(Guest),
            Hotel = sum(Hotel))

@@

```{r}
LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
LADMean <- MeanModelData(LADModelData, "LAD") %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
           AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         LowUseType =case_when(
    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  LowUseAfford =case_when(
    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor)  %>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")

@@

```{r}
MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatio2,
                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff), by = "LAD11CD") %>%
  mutate(BothHighLUP =case_when(
    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  BothHighVal =case_when(
    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  MSOALUPLADVal =case_when(
    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor
           )

 MSOAMean %>%
   #filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point()

  MSOAMean %>%
   #filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighLUP)) + geom_point()

   MSOAMean %>%
   filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()

      MSOAMean %>%
   filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighVal)) + geom_point()

  MSOAMean %>%
  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = BothHighVal)) + geom_point()

@@

Plots that help explain the data seperation
```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

@@

@@

@@

@@

#Model Combinations

@@

Outcomes <- c("HighVal", "HighLUP")
OutcomesLinear <- c("LowUsePerc", "MedianDiff")

Formulas <- c(as.formula(Reference ~ AffordRatio),
   as.formula(Reference ~ TourismDensity + AffordRatio),
      as.formula(Reference ~ AffordRatio + AffordRatio2),
   as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatio2))

@@

#LAD Model

cv <- tidy(vfold_cv(mtcars, v = 5))

cv <- tidy(vfold_cv(mtcars, v = 5, repeats = 2))

#Create sample
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))

#Create a load of classifiers
LADModels <- LinearClassifierCombiner(LADMean,  Outcomes, Formulas, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

#Create a load of linear models
LADModelsLin <- LinearClassifierCombiner(LADMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

LADModels %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            ) %>%
  ungroup %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  rename(Afford2 = IncAfford2,
         Tourism = IncTourism) %>% mutate(ModelID = rep(1:4,2))

@@

#Explore the best classifier
#There is no structure which adequately models whether A LAD will have more than the median LUP percentage
LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", TestResample, Formulas[[1]])
LADMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", TestResample, Formulas[[2]])
LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

LADMODOut %>%
  select(-statistic, -std.error) %>%
  group_by(term) %>%
  summarise_all(funs(mean, median))

@@

#MSOA Model
```{r}
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean , c(test = 0.2, train = 0.8)))

MSOAModels <-LinearClassifierCombiner(MSOAMean,  Outcomes, Formulas, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

MSOAModelsLin <- LinearClassifierCombiner(MSOAMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

MSOAModels %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            ) %>%
  ungroup %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  rename(Afford2 = IncAfford2,
         Tourism = IncTourism)

#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
LADMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", TestResample, Formulas[[4]])
LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", TestResample, Formulas[[1]])
MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

@@

>>>>

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))
rm(OAandPstCd)
```

#MSOA to LAD
```{r}
MSOAtoLAD <- EW2 %>%
  group_by(MSOA11CD, LAD11CD, LAD11NM) %>%
  summarise(TotMSOA = n(),
         Homes = sum(Homes),
         Pop = sum(Pop),
         Region = first(Region)) %>%
  arrange(-TotMSOA) %>%
  group_by(MSOA11CD) %>%
  mutate(counts = n()) %>%
  summarise(LAD11CD = first(LAD11CD),
            TotMSOA = first(TotMSOA),
            counts = first(counts),
            LAD11NM = first(LAD11NM),
            Homes = first(Homes),
            Pop = first(Pop),
            Region = first(Region)) %>%
  mutate(Region = ifelse(is.na(Region), "Wales", Region))
```

@@

##MSOA Bootstrap
Used for most of the analysis, doesn't need to be loaded as it is loaded by other functions
```{r}
setwd(file.path(basewd, "BootstrapMSOA"))
BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

##Non-Dataset LADs
This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
```{r}
#Filter out all the LADs for the data we have, ake dataframe that can be sampled
AllOtherLADsdf <- EW2 %>% rename(LSOA11CD = ECODE) %>%
  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
  mutate(LowUse = 0) 
#Bootstrap
setwd(file.path(basewd, "BootstrapAllLADs"))
BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")

#Not needed again
rm(AllOtherLADsdf)

@@

```{r}
#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(Class = CountryClass)

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio2") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

setwd(file.path(basewd, "VOA data"))

#Creates Tourism dataframe at LSOA level
Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
                          delim = "*", col_names = F) %>%
  mutate(X15 = gsub(" ", "", X15)) %>%
  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
  #filter(!is.na(LAD11CD)) %>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
   group_by(MSOA11CD) %>% #Have X6 as a grouping variable to 
  summarise(Tourism = n(),
            Guest = sum(Guest),
            Hotel = sum(Hotel))  %>%
  left_join(., MSOAtoLAD, by="MSOA11CD")

 MSOAAdjacency <- readShapeSpatial(file.path(basewd,"/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))

 test <- poly2nb(MSOAAdjacency)

 MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)

#Add MSOA codes so that they are added as the vertex names
colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd

MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")

MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")

MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")

 TourismMSOAEgo2 <- MSOAEgoList2 %>% map_df(~{
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      summarise(Ego2Tourism = sum(Tourism),
                Ego2Guest = sum(Guest),
                Ego2Hotel = sum(Hotel),
                Ego2Homes = sum(Homes))
 }) %>% mutate(Ego2TourismDens = Ego2Tourism/Ego2Homes,
               Ego2GuestDens = Ego2Guest/Ego2Homes,
               Ego2HotelDens = Ego2Hotel/Ego2Homes,
               MSOA11CD = names(MSOAEgoList1))

 TourismMSOAEgo1 <- MSOAEgoList1 %>% map_df(~{
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      summarise(Ego1Tourism = sum(Tourism),
                Ego1Guest = sum(Guest),
                Ego1Hotel = sum(Hotel),
                Ego1Homes = sum(Homes))
 }) %>% mutate(Ego1TourismDens = Ego1Tourism/Ego1Homes,
               Ego1GuestDens = Ego1Guest/Ego1Homes,
               Ego1HotelDens = Ego1Hotel/Ego1Homes,
               MSOA11CD = names(MSOAEgoList1))

Tourism <- Tourism %>%
  left_join(TourismMSOAEgo1, ., by = "MSOA11CD") %>%
  left_join(., TourismMSOAEgo2, by = "MSOA11CD") %>%
  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
         Hotel = ifelse(is.na(Hotel), 0, Hotel),
         Guest = ifelse(is.na(Guest), 0, Guest))

rm(MSOAAdjacency);rm(test);rm(MSOAAdjMat); rm(MSOAgraph); rm(MSOAEgoList1);rm(MSOAEgoList2); rm(TourismMSOAEgo1);rm(TourismMSOAEgo2)

@@

```{r}
LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
LADMean <- MeanModelData(LADModelData, "LAD") %>%
  mutate(TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         LowUseType =case_when(
    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  LowUseAfford =case_when(
    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor)  %>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")

#Amount of variance in the bootstrap samples 
#HighVal varies whilst HighLUP is fixed. However, in both of them the variables change as the affordability ratio varies. Not sure if it varies enough to change much though!
LADRefAverages <- LADModelData %>%
  group_by(LAD11CD) %>%
  summarise(HighVal = mean(ifelse(HighVal==TRUE,1,0)),
            HighLUP = mean(ifelse(HighLUP==TRUE,1,0)),
            Afford = mean(AffordRatio),
            Affordsd = sd(AffordRatio)) %>%
  left_join(., MSOAtoLAD %>% select(LAD11CD, LAD11NM)%>% distinct)

#example Affordatio bootstrap data for Chelsea. Variaince is very low
LADModelData %>% filter(LAD11CD=="E09000020") %>% ggplot(aes(x = AffordRatio)) + geom_density()

@@

```{r}
MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatioScale2,
                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff, LADMeanMedianRatio = MeanMedianRatio,
                   LowUseType), by = "LAD11CD") %>%
  mutate(BothHighLUP =case_when(
    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  BothHighVal =case_when(
    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  MSOALUPLADVal =case_when(
    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor
           )

@@

Plots that help explain the data seperation
```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

@@

quantile(MSOAMean$LowUsePerc)

@@

#Rural Analysis

The rural areas seem to be much less likely to had a negative mean difference,  but there is not enough data for the data to be used for moddelling
```{r}
LADrural <- rural %>% group_by(LAD11CD, Urban) %>%
  summarise(count = n()) %>%
  spread(key = Urban, value = count, fill = 0) %>%
  mutate(UrbanPerc = Urban/(Urban+Rural),
         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
  left_join(LADMean,.)

MSOArural <- rural %>% group_by(MSOA11CD, Urban) %>%
  summarise(count = n()) %>%
  spread(key = Urban, value = count, fill = 0) %>%
  mutate(UrbanPerc = Urban/(Urban+Rural),
         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
  left_join(MSOAMean,.)

#Almost no rural areas are classified as having a negative median difference
table(LADrural$Class,LADrural$MedianDiff>0.5)
table(LADrural$Class,LADrural$LowUseType)
2/26
42/86

table(ifelse(percent_rank(LADrural$TourismDensity)>0.5, "HighTour", "LowTour"),LADrural$HighLUP,LADrural$Class)

LADrural  %>%
  ggplot(aes(x = log(LowUsePerc), y =  log(TourismDensity), colour = Class)) + geom_point()

rm(LADrural);rm(MSOArural);rm(rural)
```

@@

cor(MSOAMea)

@@

##Model Parameters

@@

Including Mean Median is useful for LADs where the intra lad variance is large but not for MSOA where the whole area can have a high number of LUPs not just a part which occurs in lads. The effect on the lad model is to increase accuracy by only 1%

```{r}
Formulas <- c(as.formula(Reference ~ AffordRatio),
              as.formula(Reference ~ TourismDensity + AffordRatio),
              as.formula(Reference ~ AffordRatio + AffordRatioScale2),
              as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2))

#the below function is used to clearly mark the model summaries with the formular type
MarkModels <- function(df){
  df %>%
  mutate(IncAfford2 = grepl("AffordRatioScale2", Formula),
        # IncAfford3 = grepl("3", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

@@

##LAD Model

```{r}
#Create sample
set.seed(1235)
LADHighValResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
set.seed(1235)
LADHighLUPResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighLUP")

#Create a load of classifiers
LADModels <- bind_rows(LinearClassifierCombiner(LADMean,  "HighVal", Formulas, LADHighValResample),
                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample)) %>%
MarkModels

#Create a load of linear models
LADModelsLin <- bind_rows(LinearClassifierCombiner(LADMean,  "LowUsePerc", Formulas, LADHighValResample, Classifier = FALSE),
                       LinearClassifierCombiner(LADMean,  "MedianDiff", Formulas, LADHighValResample, Classifier = FALSE)) %>%
MarkModels()

LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

@@

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have high value LUPs
LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", LADHighValResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Explore the best classifier
#There The quadtratic relationship is accurately covered using this formula 
LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", LADHighLUPResample, Formulas[[4]]) %>% filter(term !="(Intercept)")
LADMODOut2 %>%  ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut2 %>%  ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))

@@

##MSOA Model
```{r}

set.seed(1235)
MSOAHighValResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighVal")
set.seed(1235)
MSOAHighLUPResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighLUP")

MSOAModels <-bind_rows(LinearClassifierCombiner(MSOAMean,  "HighVal", Formulas, MSOAHighValResample),
                       LinearClassifierCombiner(MSOAMean,  "HighLUP", Formulas, MSOAHighLUPResample))  %>%
  MarkModels()

LADModelsLin <- bind_rows(LinearClassifierCombiner(MSOAMean,  "LowUsePerc", Formulas, MSOAHighValResample, Classifier = FALSE),
                       LinearClassifierCombiner(MSOAMean,  "MedianDiff", Formulas, MSOAHighValResample, Classifier = FALSE)) %>%
  MarkModels

MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", HighValResample, Formulas[[4]])  %>% filter(term !="(Intercept)")
MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
MSOAMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

@@

#Model Bootstrap results

using the most sucessful model formula I then use the Bootstrap data to create 501 models then majority vote the response variable.
This creates a model with an overall lower accuracy but also a smaller standard deviation

set.seed(1235)
LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
test <- LADMean %>% mutate(Reference = HighVal) %>%
  ResampledModelPerf(., LADHighValResample200, Formulas[[2]])

set.seed(1235)

TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")

TestResample <- vfold_cv(LADMean, v = 5, repeats = 100, strata = "HighVal")
LADModelData2 <- LADModelData %>%
  filter(ID<102)

setwd(basewd)
if(file.exists("LADBootVoteModel.rds")){

  LADBootVoteModel <- readRDS("LADBootVoteModel.rds")

  }else{
    LADBootVoteModel <- 1:100 %>% map_df(~{ 
       print(.x)
        trainrows <- rsample2caret(TestResample)$index[[.x]]
        testrows <-  rsample2caret(TestResample)$indexOut[[.x]]

        test <- LADModelData %>% 
          mutate(Reference = as.factor(HomesMedian < LowUseMedian)) %>% 
          BootstrapResampledModelPerf(., trainrows, 
                                      testrows, 
                                      as.formula(Reference ~ TourismDensity + AffordRatio)) # creates a dataframe out predictions

      ConfOut <- LADMean %>% mutate(Reference = factor(HomesMedian < LowUseMedian, levels = c("FALSE", "TRUE")))  %>% 
        slice(testrows) %>% pull(Reference) %>%
        confusionMatrix( data =factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE")), reference = .)

          ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
          mutate(sample = .x)

    })

#has a lower mean but a much small standard deviation
LADBootVoteModel %>% SummariseModels()
